---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}
h2 {
  color: #20b2aa;
}

h3 {
  color: #20b2aa;
}

body {
  background-color: #e0f7f6;
  font-family: 'Courier New', monospace;
  max-width: 860px;
  margin: 40px auto;
  padding: 40px;
}

img {
  border-radius: 12px;
}


```
## My YouTube Video Watching Habits
This report explores my personal YouTube watching habits tracked over a period of time collected via a Google form. I tracked each video using Youtube's watch history feature. Each entry featured what type of video it was, its length, how much of the video i watched, and how engaging I found it on a scale from 1 to 5. The goal of this observational study is to find patterns in my viewing behavior, such as which types of content I watch most, and whether completing a video relates to how engaging I found it.
```{r}
library(tidyverse)

logged_data <- read_csv('https://docs.google.com/spreadsheets/d/e/2PACX-1vSzn2XXA0sB8kqTTEBpJqUtPJ61y2ayYY4IvRghKU9Ny2lZXsQO4hLwvCB0NrTyMyVz9_yjMs-aSkYB/pub?output=csv')

latest_data <- logged_data %>%
  rename(
    video_type    = `What type of video is this?`,
    minutes       = `How long is the video (minutes)`,
    seconds       = `How long is the video (seconds)`,
    watch_percent = `How much of the video did you watch?`,
    engagement    = `How engaging was the video from 1-5`
  ) %>%
  select(-Timestamp)

latest_data$total_seconds <- (latest_data$minutes * 60) + latest_data$seconds


avg_duration <- round(mean(latest_data$total_seconds) / 60, 2)
avg_engagement <- round(mean(latest_data$engagement), 2)

```
### Overview
Across all `r nrow(latest_data)` videos I logged, my average engagement score was `r avg_engagement` out of 5, and the average video I watched was `r avg_duration` minutes long .

### Videos Watched by Type
```{r}

latest_data %>%
  ggplot() +
  geom_bar(aes(x = video_type),
           fill = "#20b2aa") +
  labs(title = "Number of Videos Watched by Type",
       x = "Video Type",
       y = "Number of Videos")
```


### Engagement and Watch Behaviour


```{r}
latest_data %>%
  ggplot() +
  geom_bar(aes(x = engagement, fill = watch_percent),
           position = "dodge") +
  labs(title = "Engagement Score by Watch Percentage",
       x = "Engagement Score (1-5)",
       y = "Number of Videos",
       fill = "Watch Percentage")
```